---
title: "checker"
author: "Brandon Pazmino"
date: "12/28/2020"
output: html_document
---

```{r echo = FALSE}


stars <- read.csv("SDSS_stars.csv")
p = "https://astrostatistics.psu.edu/MSMA/datasets/asteroid_dens.dat"
sp = read.table(p, header = TRUE)
r = "https://astrostatistics.psu.edu/MSMA/datasets/NGC4406_profile.dat"
gal = read.table(r, header = TRUE) 
f = "https://astrostatistics.psu.edu/MSMA/datasets/NGC4472_profile.dat"
gal2 = read.table(f, header = TRUE) 

combo <- read.csv("COMBO17.csv")


test <- read.csv("SDSS_test.csv")
fireball <- read.csv("cneos_fireball_data.csv")
library(ggplot2)
library(highcharter)
library(magrittr)
meteor <- read.csv("Meteorite_Landings.csv")
library(plotly)
library(quantmod)
```

```{r}

p <- ggplot(sp, aes(Err, Dens, color = Asteroid)) + 
  geom_point() + 
  theme_bw()
ggplotly(p)
```

```{r}
library(highcharter)
hchart(sp, "point", hcaes(x = Err, y = Dens, group = Asteroid))

```
```{r}
hchart(sp, "line", hcaes(x = Err, y = Dens, group = Asteroid))

```
```{r}
#NGC4472 Galaxy 

hc<- hchart(gal2, type = "scatter", hcaes(radius,surf_mag),
            name = "Radius and Surface Mag of NGC4472 Galaxy",
            showInLegend = TRUE
)

hc

```
```{r}


fig <- plot_ly(fireball, x = ~Altitude_km, y = ~Velocity_km_s, z = ~Total_Radiated_Energy, marker = list(color = "blue"), showscale = TRUE )

fif <- fig %>% layout(scene = list(xaxis = list(title = "Altitude Km"),
                                   yaxis = list(title = "Velocity km/s"),
                                   zaxis = list(title = "Total Radiated Energy (J)")))

fig

```




**The Bubble Plot below is a vital ploy in understanding how Galaxies are observed through data. Here using plotly, we hage created an interactive bubble plot. our X is the Rmag which is the total red band magnitude, which is the inverted logarithmic measure of the galaxies brightness. The y is the difference between total and aperture magnitude in the R band. In other words, it is a rough measure of the size of the galaxy. the number below the coordinates of each bubble is the obect number ie the number the galaxy is classified as**

**The variable that effects the size of each bubble is mumax which is the central surface brightness of each galaxy**

**It is noted that the difference between R mag and mu_mx should be also be an indicator of the galaxy size**

```{r}




red <- plot_ly(combo, x = ~Rmag, y = ~ApDRmag, text = ~Nr, type = "scatter", mode = 'markers',
               marker = list(size = ~mumax, opacity = 0.5))
red <- red %>% layout(title = "Magnitude of Logarithmic Brightness Against size of Galaxy",
                      xaxis = list(showgrid = FALSE),
                      yaxis = list(showgrid = FALSE))

red



```



**Here we created a new variable where we took the difference in Rmag and mumax as this is also an indicator of a size of each galaxy recorded. we used this new variable as our y to compare and see how reliable it is estimating the size along with x still remaining as our RMag. For the most part, both plots seem to be similar, with a few remaining outliers in the second plot that do not occur in the first plot** 
```{r}
library(dplyr)

combo_n = mutate(combo, Diff_R_Mu = Rmag - mumax )

red2 <- plot_ly(combo_n, x = ~Rmag, y = ~Diff_R_Mu, text = ~Nr, type = "scatter", mode = 'markers', color = "red",marker = list(size = ~mumax, opacity = 0.5))

red2 <- red2 %>% layout(title = "Magnitude of Brightness against Estimated Size",
                        xaxis = list(showgrid = FALSE),
                        yaxis = list(showgird = FALSE))
red2

```

```{r}
ph <- plot_ly(combo_n, x = ~Rmag)
ph <- ph %>% add_lines(y = ~ApDRmag, name = "Difference In Total and Aperture Magnitude in R Band (Estimate of Galaxy Size)")
ph <- ph %>% add_lines(y = ~Diff_R_Mu, name = "Difference in R Magnitude Redshift Band and Central Surface Brightness (Estimated Size)") 
ph <- ph %>% layout(
  title = "Mesauring Sizes of Galaxy In Association to Redshift Band",
  xaxis = list(
    rangeselector = list(
      
    )
  ),
  rangeslider(combo_n, start = 16, end = 27)
  
)

ph


  
```



```{r}
o = "https://astrostatistics.psu.edu/datasets/censor.dat"
p = read.table(o, header = TRUE)
p
```


**The Plot below is obtained from a Dataset from stellar Astronomy. The dataset contains 39 known stars to host plants and 29 in a control sample. here is an interactive 3D chat that includes x as the stellar surface temperature of each start, y as the amount of beryllium, and z as the amount of lithium in each star. From the data, we see that the amount of beryllium in each star is correlated to the surface temperature of each star as this also gives us a broader idea of the mass in each start**

**Type 1 = Planet Hosting Star**
**Type 2 = Control Sample**


**Lets go further and assess this correlation**

```{r}
start_3d <- plot_ly(p, x = ~Teff, y = ~logN_Be, z = ~logN_Li,
                    color = ~Type,  colors = c('#BF382A', '#0C4B8E'))
start_3d <-start_3d %>% add_markers()

start_3d <- start_3d %>% layout(scene = list(xaxis = list(title = "Stellar Surface Temperature"),yaxis = list(title = "Logarithmic of Beryllium In Each Star"),
                                   zaxis = list(title = "Logarithmic of Lithium"))
)

start_3d

                      
```

```{r}
new <- plot_ly(data = p, x = ~Teff, y = ~logN_Be, type = "scatter",
               mode = 'markers', symbol = ~Type, symbols = c("circle", "x"),
               color = I("blue"), marker = list(size = 10))
new <- new %>% layout(title = "Stellar Surface Temperature Against Logarthmic Be" )

new
```


**Histogram of Stellar Surface Temperature**

```{r}
his <- plot_ly(data = p,alpha = 0.6)
his <- his %>% add_histogram(x = ~Teff)
his <- his %>% add_histogram(x = ~Teff)
his <- his %>% layout(barmode = "overlay")
his <- his %>% layout(title = "Histogram of Stellar Surface Temperature")

his

```

```{r}
line <- plot_ly(p, x = ~Teff, y = ~logN_Be, z =~logN_Li, type = "scatter3d", mode = "lines",
                opacity = 1, line = list(width = 6, color = ~Type, reverscale = FALSE))

line <- line %>% layout(title = " 3D Line Plot of Planetary Hosting Stars")

line
```


```{r}
sp_ice = subset(sp, Dens > 1 & Dens < 2)
sp_ice



```

```{r}
box_q <- plot_ly(sp_ice, x = ~Asteroid, y = ~Dens,
                 type = "bar")
box_q <- box_q %>% layout(title = "Densities of Asteroids less than 2 grams (solid Ice Material")
box_q


```
```{r}
sp_rocky = subset(sp, Dens >= 3)

box_t <- plot_ly(sp_rocky, x = ~Asteroid, y = ~Dens,
                 type = "bar")
box_t <- box_t %>% layout(title = "Densities of Asteroids less than greater or equal to 3,(Rocky Material)")
box_t

```

